\documentclass[a4paper,10pt]{article}

\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{geometry}
\usepackage{fontawesome5}

\geometry{margin=0.5in}
\pagestyle{empty}
\setlist[itemize]{left=2pt..2em, topsep=0.8pt, itemsep=3pt}

\newcommand{\resheading}[1]{
    \vspace{6pt}
    \noindent\textbf{\large\underline{#1}}\vspace{6pt}
}

\begin{document}

\begin{center}
    {\LARGE\textbf{Ismael Mueller}}\\[4pt]
    \faPhone\ +55 51 98105-8978 \quad
    \faEnvelope\ \href{mailto:ismoliveira@inf.ufrgs.br}{ismoliveira@inf.ufrgs.br} \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/ismael-mueller/}{ismael-mueller} \quad
    \faGithub\ \href{https://github.com/nvimueller}{nvimueller}
\end{center}

\resheading{EDUCATION} \\
\textbf{Federal University of Rio Grande do Sul \(|\) Porto Alegre, RS} \\
Bachelor of Science in Computer Engineering \(|\) September 2024 - Present\\
\textbf{Relevant Coursework:} Digital Circuits, Algorithm Analysis, Software Development \\

\resheading{SKILLS \& TECHNICAL TOOLS}\\
\textbf{Programming:} Python, Java, C \\ 
\textbf{Technologies:} Altera Quartus, Linux, Git, Github, JUnit \\
\textbf{Languages:} Portuguese (Native), English (C1 Advanced) \\

\resheading{EXPERIENCE}

\noindent\textbf{Physics I Tutoring \(|\) Physics Institute, UFRGS} \(|\) Sep 2025 - Dec 2025
\vspace{5pt}
\begin{itemize}
    \item Provided in-person support and assistance to students with practical exercises and theoretical concepts.
    \item Completed tutoring program with an 'A' grade awarded by the supervising professor.
\end{itemize}

\vspace{8pt}

\noindent\textbf{Reconecta Extension Project Assistant \(|\) Informatics Institute, UFRGS} \(|\) Jun 2026 - Present
\vspace{5pt}
\begin{itemize}
    \item Installed and configured Linux distributions (primarily Linux Mint) and software packages on donated hardware.
    \item Refurbished and provisioned desktops for redistribution to under-resourced university students and campus housing.
\end{itemize}

\vspace{8pt}

\resheading{PROJECTS}

\noindent\textbf{Neander Theoretical Processor} \(|\) Digital Circuits, Altera Quartus \(|\) Jun 2026
\vspace{5pt}
\begin{itemize}
    \item Reproduced a functional Neander 8-bit processor using a hierarchical block diagram design methodology within Altera Quartus.
    \item Implemented the core instruction set, enabling foundational CPU operations such as arithmetic summation, memory loading, and logical operations.
    \item Designed and integrated a custom hardware circuit on an FPGA board to output and visualize real-time processor execution data on a physical display.
\end{itemize}

\vspace{8pt}

\noindent\textbf{Command-Line Task Management Tool} \(|\) Python \(|\) Jul 2026
\vspace{5pt}
\begin{itemize}
    \item Developed a pip-installable command-line application using Python's \texttt{argparse} library, creating a globally accessible \texttt{pydo} command for streamlined terminal workflows.
    \item Programmed core task management functionalities - including commands to add, list, rename, and complete tasks - with persistent data storage utilizing a local CSV file architecture.
    \item Packaged the project for straightforward deployment, enabling users to clone the repository and install the tool natively for direct execution without manual script invocation.
\end{itemize}
 
\end{document}
